LAGOS lake depth

### 2020-03-24 README.Rmd
add stand-in title
towards a complete data dictionary

## Bathymetry manuscript

@@

@@

dt <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field")) 
```
</details> &nbsp;

Data: [bathymetry derived lake geometry](data/00_bathy_depth/bathy_geometry.csv)

dt <- read.csv("data/00_bathy_depth/bathy_geometry.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
</details>

>>>>

## Bathymetry data from thousands of lakes show that difficulty modeling in-lake slope limits lake depth prediction

@@

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# see scripts/99_make_taxonomy.R
library(dplyr)
taxonomy <- read.csv("data/taxonomy.csv", 
                     stringsAsFactors = FALSE)
dt       <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", 
               stringsAsFactors = FALSE) %>%
  names() %>%  as.data.frame() %>%  setNames("col_name") %>%
  left_join(taxonomy)
knitr::kable(dt) 
```
</details> &nbsp;

Data: [bathymetry derived lake geometry](data/depth_predictors.csv)

@@

dt <- read.csv("data/depth_predictors.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
</details>
